---
title: "Model"
author: "Ben Wallace, Lily Zhu"
date: "10/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(broom)
library(knitr)
library(data.table)
library(leaps)
library(rms)
library(Sleuth3)
```


```{r read data}
unemployment_change <- fread(here("data", "unemployment-change.csv"))
mobility_avg <- fread(here("data", "mobility-avg.csv")) %>%
  mutate(county = sub_region_2) %>%
  select(-sub_region_2)
socioeconomic <- fread(here("data", "socioeconomic.csv")) %>%
  mutate(county = area_name) %>%
  select(-area_name)
unemployment_change
```

## Merge data

```{r}
merged_data <- unemployment_change %>%
  inner_join(mobility_avg, by = "county") %>%
```


```{r}
#inner_join(socioeconomic, by = "county")

set.seed(0)
sample_data <- sample_n(merged_data, 500)

sample_data
```

```{r}
ggplot(data = sample_data, mapping = aes(x = unemployment_change)) +
  geom_bar()
```

## EDA

```{r}
merged_data %>%
  ggplot(aes(y = unemployment_change, x = retail_avg)) +
  geom_point()
```

```{r}
model <- lm(unemployment_change ~ retail_avg + 
              grocery_avg + 
              parks_avg + 
              transit_avg + 
              workplaces_avg + 
              residential_avg, 
            data = merged_data)

model %>%
  tidy(conf.int = TRUE) %>%
  kable(digits = 3)
```

## Questions
- What is the relationship between ___ and ___? What does this say about the future of unemployment during the future of this pandemic, which experts believe will continue into the next years?
- Given the relationship between these variables, what is the expected unemployment rate of North Carolina counties?

## Predictors:
- resilience:

## Response:
- unemployment rate:

## EDA:

See .rmd files in folder.

## Model: We will use a multiple linear regression model with the following form:

> unemployment rate = resilience + __ + __ + __ + __

#### Output:

```{r}
full_model <- lm(unemployment_change ~ .,data = sample_data)

# model_aic <- step(full_model, direction = "backward")
```


