---
title: "Untitled"
author: "Ben Wallace"
date: "10/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read data}
unemployment <- read.csv("../data/Unemployment.csv")
```

## Merge data
```{r}
unemployment <- unemployment %>% 
  mutate(county = sapply(strsplit("Autauga County, AL", ","), "[", 1))

mobility <- mobility %>% 
  mutate(county = sub_)
```

```{r}
merged_data <- inner_join(unemployment, mobility, 
                           by = "")
```

### Questions
- What is the relationship between ___ and ___? What does this say about the future of unemployment during the future of this pandemic, which experts believe will continue into the next years?
- Given the relationship between these variables, what is the expected unemployment rate of North Carolina counties?

### Predictors:
- resilience:
-
### Response:
- unemployment rate:

### EDA:

See .rmd files in folder.

#### Conclusions from EDA:

### Model: 

We will use a multiple linear regression model with the following form:

> unemployment rate = resilience + __ + __ + __ + __

### Model Selection

Using Akaike's Information Criterion (AIC)

```{r}
### Insert code for AIC here
```

#### Output:


##

